Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-27 paper.tex
edit lemma 1

\begin{lemma}
For those user whose utility difference between their best arm and the second best arm is at least $2m\lambda$, the probability that myopic action can incur regret at any time $t\in [t_{n-1},t_{n}-1]$ in the $n^{th}$ round is bounded above by $24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
\label{round:prob}
\end{lemma}

>>>>

\begin{lemma}
$P(A_t\neq B(\theta_t)|t\in [t_n, t_{n+1}-1],\theta_t\cdot(u_{B(\theta_t)}-u_{\hat{B}(\theta_t)})\geq 2m\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
\label{round:prob}
\end{lemma}
